---
title: "Hydraulic Geom
"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ggplot2)
library(knitr)

```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
stream_stats<-read.csv("D://GEOG_4300/1111111.csv")


  colnames(stream_stats)[colnames(stream_stats)=="Name.of.Channel"] <- "Coordinates"
  
  
```

```{r}
ggplot(stream_stats, aes(x=Basin.area, y=Channel.Width))+
  geom_point(size=3)+
  scale_y_log10()+
  scale_x_log10()+
  theme_bw()+
  labs(x="Basin Area (square miles)", y="Channel Width (feet)")+
  geom_smooth(method = lm, se = FALSE, )
  
```


```{r}
kable(stream_stats)
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
